### 2020-02-14 README.Rmd
Reformat README to cater for the future addition of content about validating dictionary-based methods
Make create_oolong die when input_model and input_corpus are NULL.

@@

## Example

### Word intrusion test

@@

### Topic intrusion test

@@

## Suggested workflow

@@

## About the p-values

@@

## About Warp LDA

@@

>>>>

The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

| input\_model | input\_corpus | output                                                                          |
|--------------|:-------------:|---------------------------------------------------------------------------------|
| Not NULL     | NULL          | oolong test for a topic model with word intrusion test                          |
| Not NULL     | Not NULL      | oolong test for a topic model with word intrusion test and topic intrusion test |
| NULL         | Not NULL      | oolong test for creating gold standard                                          |
| NULL         | NULL          | error                                                                           |

@@

## Validating Topic Models

#### Word intrusion test

@@

#### Topic intrusion test

@@

### Suggested workflow

@@

### About the p-values

@@

### About Warp LDA

@@

## Validating Dictionary-based Methods

### Creating gold standard

`trump2k` is a dataset of 2,000 tweets from @realdonaldtrump.
